The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-15 analysis/paper/paper.qmd
Add functions to calculate top n words

```{r}
# Which are the top 20 most frequently used words in each thesis?
emu_theses_top_20 <- emu_theses_words %>%
  group_by(title) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50) %>%              ### filter words with a minimum count
  ungroup() %>% 
  mutate(word = reorder(word, n))

# Which are first 5 most frequently used words in each thesis?
emu_theses_first_5 <- emu_theses_words %>%
  count(title, word) %>% 
  group_by(title) %>% 
  arrange(desc(n)) %>% 
  slice(1:5)

# Which theses contain "fabric" in the top 20 most frequently used words?
emu_theses_top_20 %>% 
  filter(word == "fabric")

>>>>

Counting frequencies of words per document
```{r}
# Which are the top n most frequently used words in each thesis?
top_n_word_count_per_document(data = emu_theses_words, 
                              top_n = 3, 
                              title_col = 'title', 
                              word_col = 'word')
```

```{r}
# Which are the top n most frequently used words in all theses`?
top_n_word_count_per_corpus(emu_theses_words, 5, "word")
```

```{r}
# Which are first 5 most frequently used words in each thesis?
emu_theses_first_5 <- emu_theses_words %>%
  count(title, word) %>% 
  group_by(title) %>% 
  arrange(desc(n)) %>% 
  slice(1:5)
```

```{r}
# Which theses contain "fabric" in the top 20 most frequently used words?
emu_theses_top_20 %>% 
  filter(word == "fabric")
